\bf{Information Brochure}\\
\textcolor{red}{\large BRIEF HISTORY OF THE INSTITUTE}\\
\bf{Guru Nanak Dev Engineering College was established by the Nankana Sahib Education Trust (NSET) Ludhiana. The Nankana Sahib Education was founded in memory of the most sacred temple of Sri Nankana Sahib, birth palace of Sri Gurur Nanak Dev Ji. Shiromani Gururdwara Parbandhak Committee, Amritsar, a premier organisation of Univarsal Brotherhood, was the main force behind the mission of "Removal of Economic Backwardness through Technology". With this mission, a Polytecnhic was started in 1953 and Guru Nanak Dev Engineering College was established in 1956. Nankana Sahib Education Trust resolved to uplift the vast weaker section of Indian polity comprising of Rural India by admitting 70\% students every year from rural areas. This commitment was made to nation on 8th April, 1956, the day foundation stone of the College building was laid by Dr. Rajendra Prasad Ji, the first president of India. Nearly 10,000 Graduate and 2000 Post-Graduate Engineers have passed out from this college during the last 49 years and are successfully employed in India and abroad. This college is now ISO 9001:2000 certified. Five branches of Engineering as listed below are Accredited by National Board of Accreditation, (NBA) AICTE, New Delhi. College is also supported under FIST and TEQIP scheme of Govt. of India and is a QIP centre of PhD research.
  }\\
\textcolor{red}{\bf\large{UNDER GRADUATE COURSES}}\\
\begin{tabular}{|l|}
\hline
1. Civil Engineering \\ \hline
2. Mechanical Engineering\\ \hline
3. Electrical Engineering\\ \hline
4. Electronics & Communication Engineering\\ \hline
5. Computer Science Engineering\\ \hline
6. Information Technology\\ \hline
7. Production Engineering\\ \hline
\end{tabular}\\
Following Posgraduate Courses are running in different departments: \\
\begin{tabular}{|p{0.25in}|p{0.4in}|p{0.4in}|p{0.6in}|p{0.6in}|p{0.6in}|p{0.25in}|p{0.25in}|}
\hline
S.No. & Civil Engg. Deptt. & Mechanical Engg. Deptt. & Electrical Engg. Deptt. & Comp. Sc. Engg. & Electronics Engg. Deptt. & MBA & MCA\\ \hline
\end{tabular}
\textcolor{red}{\bf{\Large TESTING & CONSULTANCY CELL}}\\
\bf{Testing & Consultancy Cell was established in the year 1979 with a basic aim to provide quality service for technical problems at reasonable and affordable rates as a service to society in general and Engineering fraternity in particular. Ours is a pioneer institute providing Consultancy Services in the States of Punjab, Haryana, Himachal, J&K and Rajasthan. Various Major Clients of the Consultancy Cell are as under:
\begin{enumerate} \addtolength{\itemsep}{-0.9\baselineskip}
\item Larson & Tubro \item Multi National Companies like AFCON & PAULINGS,
\item Power Grid Corporation of India 
\item National Thermal Power Corporation 
\item National Building Construction Co. 
\item Northern Railway, Govt. of India 
\item Municipal Corporations of Punjab & Chandigarh 
\item Military Engineering Services 
\item Punjab State Electricity Board 
\item Punjab Mandi Board 
\item Punjab Police Housing Corporation 
\item Punjab Health System Corporation 
\item Punjab State PWD (B & R, Public Health and Irrigation) 
\item Punjab Water Supply & Sewerage Board 
\item Punjab State Education Board, Mohali 
\item Hindustan Petroleum Corporation Limited 
\item National Fertilizers Ltd. 
\item PUNSUP 
\item Postal & Telecom Department, Govt. of India  
\item Sonalica Tractors & Cars Ltd, (Punjab & H.P) 
\item Big Industrial Houses like Hero Cycles, Oswal Woollen Mills, OCM Woollen Mills, Vardhman Knitting Yarn Mills etc. 
\item BBMP, Charkhi Dadri (Haryana) 
\item  INDIAN Depot Oil AIR FORCE Halwara State
\item I.O. Limited Jalandhar
\end{enumerate}}\\
\textcolor{red}{\bf{\Large CIVIL ENGINEERING }}\\
\textcolor{green}{\bf \large LABORATORIES}\\
\textcolor{blue}{Geo-technical Lab}\\
\large Bearing Capacity of Soil by \\
Plate Load Test\\
Standard Penetration\\
\large Pile Test\\
\large Chemical Analysis of Soil\\
\large Consolidation Test\\
\large Compaction Test \\
\large Field Density Test \\
\large Relative Density Test\\
\large Computerized Triaxil Shear Testing Machine\\
\large Rapid moisture meter\\
\large Permeability Test\\
\large Particle Size Analysis\\
\large Consistency Limits\\
\large Liquefaction analysis\\
\large Swell Test\\
\textcolor{blue}{Transportation Engineering Lab}\\
\large CBR Test - Digital Equipment\\
\large Abrasion Value Test \\
\large Crushing Value Test \\
\large Impact Value Test\\
\large Softening Point Test of Bitumen \\
\large Shape Test \\
\large Ductility Test of Bitumen\\
\large Specifc Gravity Test \\
\large Penetration No. of Bitumen\\
\large Rougho Meter \\
\large Benkleman 'Beam Apparatus\\
\large Marshal stability Test\\
\textcolor{blue}{Material Testing Lab}\\
\large Testing of Materials like Cement, Steel, Sand, Aggregates, Concrete Cubes, Flooring Tiles, Pavers, Bricks, Tiles etc.\\
\large Checking Strength of Hardened Concrete by Non-Destructive Test like \\
Ultra Sonic Technique\\
Rebound Hammer Technique\\
\large Chemical Analysis of Cement & Concrete\\
\large Flexural Strength of Concrete Beams\\
\large Timber (Water Content & Flexural Strength)\\
\textcolor{blue}{Survey Lab}\\
\large Preparation of Contour Map with the use of Total Station\\
\large Marking of Alignment of Different Structures\\
\large Survey Plan & Leveling\\
\large Preparation of L Section & X-section\\
\large Preparation of Digital Maps\\
\textcolor{blue}{Environmental Lab}\\
\large Analysis of Water Samples for Drinking, Construction & Boiler\\
\large Analysis of Waste Water\\
\large Treatability Studies for Industial Wastes\\
\large Design & Commissioning of Effluent Treatment Plants\\
\large Preparation of Project Fesibility Reports for ETPs \\
\large Design of Air Pollution Control Devices \\
\large Adequacy reports for Existing/Designed ETPs & APCDs \\
\large Environmental Auditing\\
\large Environmental Impact Assessment \\
\textcolor{blue}{Engineering Design}\\
\large Structural Design of Reinforced Concrete Structures Like Industrial Structure, Institutional Building, Other Buildings, Residential Building, OHSR & Treatment Plant \\
\large Structural Design of Steel Structures \\
\large Structure Design of Masonry Structures\\
\large Mix Design \\
\large Pavement Design \\
\textcolor{blue}{Other Services}\\
\large Estimation & Costing of Project \\
\large Supervision & Quality Control \\
\large Calibration of different Equipments\\
\textcolor{green}{\bf\large TESTING TEAM}\\
\emph{Geo-Technical Engg. }\\
Dr. J.N.Jha, Ph.D. \\
Er. Harjinder Singh, M.E. \\
Er. Kulbir Singh Gill, M.E. \\
Dr. B.S. Walia, Ph.D \\
Er. Gurdeepak Singh, M.Tech. \\
\emph{Structural Engg.}\\
Dr. Hardeep Singh Rai, Ph.D.\\
Dr. Harpal Singh, Ph.D.\\
Dr. Harvinder Singh, Ph.D\\
Er. Prashant Garg, M.E.\\
\emph{Highway Engg.}\\
Er. Kulbir Singh Gill, M.E.\\
Er. Prashant Garg, M.E.\\
\emph{Material Testing}\\
Er. Kanwarjit Singh Bedi, M.Tech. \\
Dr. Jagbir Singh, Ph.D \\
\emph{Survey}\\
Dr. B.S. Walia, M.E.\\
Er. Kanwarjit Singh Bedi, M.Tech. \\
\emph{Environmental Engg.}\\
Dr. R.P. Singh, Ph. D. \\
Er. Puneetpal Singh Cheema, M.E.\\
\textcolor{red}{\bf{\Large ELECTRICAL ENGINEERING}}\\
\textcolor{green}{\bf \large LABORATORIES}\\
\textcolor{blue}{Electrical Machines }\\
\textcolor{blue}{High Voltage}\\
\textcolor{blue}{Power Electronics and Microprocessors }\\
\textcolor{blue}{Electrical Measurement }\\
\textcolor{blue}{PowerSystems and Control}\\
\textcolor{blue}{Basic Electrical Engg.}\\
\textcolor{blue}{Computer}\\
\textcolor{blue}{Applied Electronics}\\
\textcolor{green}{\bf\large TESTING TEAM}\\
Er. Jaswinder Singh, M.E.\\
Er. Khushdeep Singh, M.E.\\
Er. Rupinderjit Singh, B.E.\\
Er. Preetinder Singh, B.E. \\
Er. Kanwardeep Singh, M.Tech. \\
Er. Gagandeep Singh Sodhi, M.Tech.\\
Er. Navneet Singh Bhangoo, M.Tech.\\
\textcolor{green}{\bf FACILITIES}\\
Design, Development and testing facilities for power electronics gadgets like Inverters, Choppers etc.\\
Testing & verification of rating for electric motors upto 100 H.P.\\
esting of Insulators for impulse and power frequency, dry and wet, Flashover and Breakdown voltage.\\
Testing of Transformer oil at power frequency.\\
Testing and Calibration of various electrical measuring  instruments.\\
Detection & Localization of Underground Cable faults.\\
Determination of Earth Resistivity & Earth Resistance.\\
 Electrical Energy Auditing of Industrial & Commercial Houses. \\
Design of Modern Lighting System for industrial & commercial houses. \\
Design and implementation of digital controllers for  process industry.\\
Installation & layout Design for subslations upto 66 K.V.\\
\textcolor{red}{\bf{\Large ELECTRONICS ENGINEERING}}\\
\textcolor{green}{\bf \large LABORATORIES}\\
\textcolor{blue}{Communication and T.V.}\\
\textcolor{blue}{Micro-wave}\\
\textcolor{blue}{Digital Electronics and Project}\\
\textcolor{blue}{Electronics Design and Automation Lab}\\
\textcolor{blue}{Microprocessor and Hardware}\\
\textcolor{blue}{Fiber optics & Multimedia}\\
\textcolor{green}{\bf\large TESTING TEAM}\\
Er. Nirmal Singh Grewal M.Tech.\\
Er. Ameeta Seehra, M.Tech.\\
Dr. S.S. Gill, Ph.D.\\
Er. Narwant Singh, M.Tech.\\
Er. B.S. Dhaliwal, M.Tech.\\
Dr. Munish Rattan, Ph.D. \\
Er. Baljeet Kaur \\
\textcolor{green}{\bf FACILITIES}\\
Projects based on installation, interfacing, programming and testing on Micro controllers, Microprocessors, and PLCs. \\
Industrial Electronics Based Application and trouble shooting \\
Fuzzy Logic Based control systems \\
PCB Design and Development. \\
Projects on Antenna (Simulation & Design) \\
\textcolor{green}{\bf SHORT TERM TRAINING}\\
VLSI Design \\
Programming and Hardware Implementation using VHDL \\
Electronic circuit design and analysis using ORCAD/PSPICE \\
Training module on Fiber optics \\
Training module on Digital Signal processing \\
Training module on Wireless communication systems\\
Training module on MAT LAB\\
\textcolor{red}{\bf{\Large MECHANICAL ENGINEERING & PRODUCTION TECHNOLOGY}}\\
\textcolor{green}{\bf \large LABORATORIES}\\
\textcolor{blue}{Heat Engines & Thermal Sciences}\\
\textcolor{blue}{Metrology & Mechanical Measurements}\\
\textcolor{blue}{Heat Transfer }\\
\textcolor{blue}{Hydraulic Machines}\\
\textcolor{blue}{Machine Tools }\\
\textcolor{blue}{Metal Forming }\\
\textcolor{blue}{CAM and Automation }\\
\textcolor{blue}{Dynamics of Machines }\\
\textcolor{blue}{Metallurgy and Heat Treatment}\\
\textcolor{blue}{Computer Aided Design (CAD)}\\
\textcolor{green}{\bf\large TESTING TEAM}\\
Dr. Sehijpal Singh, Ph.D .\\
Dr. Paramjit Singh, Ph.D.\\
Dr. Harwinder Singh, Ph.D.\\
Dr. Rupinder Singh, Ph.D.\\
Er. Jatinder Kapoor, M.Tech.\\
Er. Ravi-Inder Singh, M.Tech. \\
Er. Prem Singh, M.Tech. \\
Er. G.S. Brar, Ph.D.\\
\textcolor{green}{\bf FACILITIES}\\
\emph{Engineering Design  & CAD}\\
Design verification/validation of stuctural design of Multiaxle trailers, cranes and other mechanical components. \\
Product conceptualization & 3-D Modeling of Industrial components, computer aided drawing generation through reverse Engineering. \\
Design of press tools, moulds and dies for casting & plastic injection dies. \\
Design of Mechanisms. \\
Design & Testing of Hoists, Lifts, Lifting mechanisms & safely provision etc. \\
Pressure Gauge & Pipe Testing \\
\emph{Manufacturing & Industrial Engineering}\\
Optimisation of Industrial/Manufacturing processes. \\
Operation Management (inventory Management & Control, Material Management & Line Balancing etc.) \\
Supply Chain Management & Waste Minimisation\\
Metallurgical & Micro structural analysis\\
 Capacity Utilization \\
\emph{Thermal Engineering}\\
Refrigeration & Air Conditioning system design. \\
Fuel Testing & Combustion characterstics of different fuels. \\
Energy Management & Auditing. \\
Performance Testing of Centrifugal Pumps, Submercible Pump. \\
Engine performance testing. \\
Thermal properties testing of different material. \\
\textcolor{green}{\bf SHORT TERM TRAINING}\\
Training Module on Product Design, 3D Modeling & CAD, Lean & Supply Chain Management, Six-Sigma, Thermal System design & optimisation,  Non-Traditional  Manufacturing, Maintenance & Reliability.\\
\textcolor{red}{\bf{\Large COMPUTER SCIENCE ENGINEERING & INFORMATION TECHNOL}}\\
\textcolor{green}{\bf \large LABORATORIES}\\
\textcolor{blue}{Operating System Lab-I}\\
\textcolor{blue}{Operating System Lab-II}\\
\textcolor{blue}{Project lab-I}\\
\textcolor{blue}{Project lab-II}\\
\textcolor{blue}{Hardware - Lab}\\
\textcolor{blue}{Software Lab-I}\\
\textcolor{blue}{Software Lab-II}\\
\textcolor{blue}{Web Development Lab}\\
\textcolor{blue}{DBMS Lab}\\
\textcolor{blue}{Computer Network Lab}\\
\textcolor{blue}{Research Lab}\\
\textcolor{green}{\bf\large TESTING TEAM}\\
Er. Akshay Girdhar, M.Tech. (IT)\\
Er. Amanpreet Singh Brar, M.Tech. (CSE)\\
Er. Parminder Singh, M.Tech. (CSE)\\
Er. Jasbir Singh Saini, M.Tech. (IT)\\
Er. Kulwinder Singh Mann, M.Tech. (IT)\\
Er. Manpreet Singh, M.Tech. (CSE)\\
Er. Kiran Jyoti, M.Tech. (CSE)\\
Er. Amandeep Kaur Sohal. M.Tech. (CSE)\\
Er. Raninder Kaur, MS (S/W Systems)\\
Er. Sumeet Kaur, M.Tech. (CSE)\\
Er. Amit Kamra, M.Tech. (IT)\\
Er. Vivek Thapar, M.Tech. (IT)\\
Er. Sukhjit Singh, M.Tech. (CSE)\\
Er. Pankaj Bhambri M.Tech. (CSE)\\
Er. Kamaljit Kaur Dhillon M.Tech. (CSE)\\
Parminder Kaur Wadhwa M.Tech (CSE)\\
\textcolor{green}{\bf FACILITIES}\\
Networking-installation and Maintenance\\
Hardware fault Diagnosis & Testing \\
Installation & Configuration of Servers \\
Desktop publishing (DTP) \\
Computerized layout plan \\
Software packages development for Automation\\
\textcolor{green}{\bf SHORT TERM TRAINING}\\
Training Module on Python/PHP\\
Training Module on Oracle/SQL \\
Training Module on Java \\
Training Module on C++, C \\
Training Module on Networking \\
Training Module on Hardware \\
\textcolor{red}{\bf{\Large APPLIED SCIENCES}}\\
\textcolor{green}{\bf \large LABORATORIES}\\
\textcolor{blue}{Applied Chemistry Lab}\\
\textcolor{green}{\bf\large TESTING TEAM}\\
Dr. R.P. Singh, Ph. D.\\
Er. Punit pal Singh Cheema, M.Tech\\
\textcolor{green}{\bf FACILITIES}\\
 Chemical Analysis of Cement (Silica, Calcium oxide, Magnesium oxide, Iron oxide, Chromium oxide, Loss on ignition, Insoluble residue) \\
Cheimical Analysis of Cement Mortar (Ratio of cement and sand)\\
Chemical Analysis of Cement Concrete (Ratio of cement, sang, aggregate)\\
Test of Water (Chlorides, sulphates, pH value dissolved  solids, hardness, alkalinity) \\
Chemical Analysis of Soil/Sand (Chorides,  sulphates, Calcium carbonate) \\
Chemical Analysis of Coarse/Fine  Aggregates (Sodium and magnesium sulphate, clay lumps, fine material, deleterious materials) \\
Chemical Analysis of Boiler water \\
Flash Point of Fuels  \\
Penetration Number of Lubricant \\
\textcolor{red}{\bf{\Large CENTRAL WORKSHOP}}\\
\textcolor{green}{\bf \large LABORATORIES}\\
\textcolor{blue}{Machine Shop}\\
\textcolor{blue}{Fitting Shop}\\
\textcolor{blue}{Electric Shop}\\
\textcolor{blue}{Carpentry Shop}\\
\textcolor{blue}{Foundry Shop}\\
\textcolor{blue}{Blacksmithy Shop}\\
\textcolor{blue}{Welding Shop}\\
\textcolor{blue}{Sheet Metal and Plumbing Shop}\\
\textcolor{green}{\bf\large TESTING TEAM}\\
Er. Jasmaninder Singh Grewal M.E.\\
Er. Ranjit Singh\\
\textcolor{green}{\bf FACILITIES}\\
Material handling\\
Machines Maintenance (Lathe & Milling)\\
Faults Finding in Electric Motors \\
Consultancy of Welding of Odd Job. \\
\textcolor{green}{\bf SHORT TERM TRAINING}\\
Fault Finding and Repair of Domestic Appliances\\
Material Metrology and Engineering inspection \\
Carpenter \\
Pattern Making \\
Motor Winding\\
Welder \\
Machinist\\
Turner \\
Fitter\\
Moldel\\
Fabrication \\
\textcolor{red}{\bf{\Large MBA}}\\
\textcolor{green}{\bf\large TESTING TEAM}\\
Dr. Sukhdev Singh, MBA, M.Com, DPMIR, Ph.d\\
Prof. Parampal Singh, M.Sc., MBA \\
Amanjot K. Gill, MCBA \\
Prof. H.S. Dhall\\
\textcolor{green}{\bf AREA OF CONSULTANCY}\\
Financial Management\\
Marketing Management\\
Human Resource Management\\
